LDM-503-1 & 2017-11-30 & NCSA & \textbf{Science Platform with WISE data in PDAC}
SUIT continues PDAC development, adding the WISE data, further exercising the DAX dbserv and imgserv APIs, and taking advantage of metaserv once it becomes available
\\ \hline
LDM-503-2 & 2017-11-30 & NCSA & \textbf{HSC reprocessing}
Validate the data products with the LSST stack match or improve upon HSC products.
 Validate the ops platform in NCSA, including installing the stack, starting and stopping production.
 Generate a validation data set for weekly integration and other tests.
\\ \hline
LDM-503-3 & 2017-11-30 & NCSA & \textbf{Alert generation validation}
Validate the alert generation stack performance on several DECam and HSC datasets.
\\ \hline
LDM-503-4 & 2018-02-01 & NCSA & \textbf{Aux Tel DAQ integration functionalty test}
The production Aux Tel data acquisition hardware should be available in Tucson in 2018-02. We should prepare by testing the adjacent archive systems.
\\ \hline
LDM-503-4b & 2018-02-12 & NCSA & \textbf{Test Report: Aux Tel DAQ interface Integration Verification and Spectrograph Operations Rehearsal}
The production Aux Tel data acquisition hardware should be available in Tucson in 2018-02. We should test integration with the adjacent archive systems.
\\ \hline
LDM-503-5 & 2018-05-31 & NCSA & \textbf{Alert distribution validation}
Validate alert distribution system and mini-broker fed by live or simulated live data.
\\ \hline
LDM-503-6 & 2018-06-30 & NCSA & \textbf{DM ComCam interface verification readiness}
ComCam will be in Tucson on 2018-07-24. The DM system must be ready to deal with it.
\\ \hline
LDM-503-7 & 2018-08-31 & NCSA & \textbf{Camera data processing}
Partial camera data should be available to DM July 31st. We plan to test DM stack with it.
\\ \hline
LDM-503-8 & 2018-11-30 & NCSA & \textbf{Spectrograph data acquisition}
Demonstrate that we can acquire (and process?) data from the spectrograph.
\\ \hline
LDM-503-9 & 2018-11-30 & NCSA & \textbf{Verification tests in advance of pre-ops rehearsal for commissioning \#1}
Test how the system will run during commissioning.
 Chuck requests that this initial test focus on ISR.
\\ \hline
LDM-503-10 & 2019-02-28 & NCSA & \textbf{DAQ validation}
There is a project Milestone that DAQ/DM/Networks are available March 15th. We need to run tests in Feb to show this is ready.
\\ \hline
LDM-503-11a & 2019-10-20 & NCSA & \textbf{DM ComCam operations readiness}
ComCam will be in use in Nov . The DM system must be ready to deal with it.
\\ \hline
LDM-503-11 & 2019-10-31 & NCSA & \textbf{Verification tests in advance of pre-ops rehearsal for commissioning \#2}
More complete commissioning rehearsal: how do the scientists look at data? How do they provide feedback to the telescope? How do we create/update calibrations?
 Exercise control loops.
\\ \hline
LDM-503-12 & 2020-01-31 & NCSA & \textbf{Verification tests in advance of pre-ops rehearsal for commissioning \#3}
Dress rehearsal: commissioning starts in April, so by this stage we should be ready to do everything needed.
\\ \hline
LDM-503-13 & 2020-11-30 & NCSA & \textbf{Ops rehearsal DRP (ComCam data)}
ComCam data will now be available. Demonstrate its use in producing a data release.
\\ \hline
LDM-503-14 & 2021-03-31 & NCSA & \textbf{DM Software for Science Verification}
Science Verification starts in April. Demonstrate that all required DM software is available.
\\ \hline
LDM-503-15 & 2021-11-30 & NCSA & \textbf{Ops rehearsal DRP (SV data)}
Science Verification data will now be available. Demonstate its use in producting a data release.
\\ \hline
LDM-503-16 & 2022-02-28 & NCSA & \textbf{Verification tests in advance of full scale ops rehearsal \#1}
Test readiness for operations.
\\ \hline
LDM-503-17 & 2022-09-30 & NCSA & \textbf{Verification tests in advance of full scale ops rehearsal \#2}
Confirm readiness for operations.
\\ \hline
