\documentclass[lsstdraft,DM,STP,toc]{lsstdoc}
\usepackage{texmf/pgfgantt}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{booktabs}
\colorlet{dmyellow}{yellow!50!white}
\colorlet{dmblue}{cyan!50!white}
\colorlet{dmorange}{orange!50!white}
\colorlet{dmgreen}{green!50!white}
\colorlet{dmred}{red!50!white}


%set the WP number or product here for the requirements
\def\product{Data Management}
\def\cycle{S17}

\setDocCompact{true}

%Product name first in title
\title    [Test Plan]  { \product ~Test Plan}

\author   {William O'Mullane, John Swinbank, Mario Juric, Frossie Economou, Gabriele Comoretto, Leanne Guy}                % the author(s)
\setDocRef      {LDM-503} % the reference code
\setDocDate     {\today}              % the date of the issue
\setDocUpstreamLocation{\url{https://github.com/lsst/LDM-503}}
%
% a short abstract
%
\setDocAbstract {
This is the  Test Plan for \product. In it we define terms associated with testing and further test specifications for specific items.}

%
%
\setDocChangeRecord{%
	\addtohist{}{2017-01-13}{First draft}{William O'Mullane}
	\addtohist{1.0}{2017-06-30}{First approved release.}{William O'Mullane}
	\addtohist{1.1}{2017-07-04}{Minor cleanups for review. Approved in \jira{RFC-358}.}{W.~O'Mullane}
	\addtohist{1.2}{2017-07-19}{Milestone alignment with plan }{W.~O'Mullane}
	\addtohist{}{2018-06-18}{Milestone alignment with PMCS and derived from it }{J.D.~Swinbank}
	\addtohist{1.3}{2018-06-18}{Approved in \jira{RFC-492}}{J.D.~Swinbank}
	\addtohist{1.4}{2018-07-17}{Correct test specifications for LDM-503-04, 04b, 05, 08b. Link Pipelines releases to \citeds{LDM-564}. Approved in \jira{RFC-501}.}{J.D.~Swinbank}
	\addtohist{1.5}{2018-11-13}{Include updated document tree. Update milestones for month end September 2018. Describe approach to managing tests in Jira.}{W.~O'Mullane; J.D.~Swinbank; G.~Comoretto}
	\addtohist{1.6}{2019-07-12}{Updated schedule based on PMCS for month end May 2019.  Updated description and link to test plan \& report for LDM-503-07 \& LDM-503-09a. Add milestone LDM-503-10a. Overhaul milestone descriptions following input from product owners and T/CAMs.}{J.D.~Swinbank}
	\addtohist{1.7}{2020-08-18}{Eliminate mention of deprecated low-level test specifications (all those other than LDM-540). Update milestone descriptions and schedule to be current as of end June 2020. Clarified requirements verification using available data (\jira{DM-22089}). \jira{RFC-708}}{J.D.~Swinbank; L.P.~Guy}
	\addtohist{1.8}{2021-06-11}{Refresh for review - include GEN3. Approved in \jira{RFC-781} }{W.~O'Mullane}

}


\begin{document}
%
% the title page
%
\maketitle


\input{body}
\end{document}
