\begin{longtable} {|l|l|p{0.7\textwidth}|}
	\caption{Operations rehearsals for Ops validation of DM \label{tab:ors}}\\  %%%%%
	\hline
\textbf{Date/Freq} &\textbf{Location}& \textbf{Title, Description} \\ \hline

Oct 2018 &  NCSA & \textbf{Operations rehearsal for commissioning }
	With TBD weeks commissioning (lets say a week) -- pick which parts of plan we could rehearse.
	Chuck suggests Instrument Signal Removal should be the focus of this (or the next rehearsal).
	\\ \hline
Oct 2019 & NCSA &  \textbf{Operations rehearsal \#2 for commissioning}
More complete rehearsal -- where do the scientist look at quality data? How do they feed it back to the Telescope ?
How do we create/update calibrations ? Exercises some of the control loops.
\\ \hline
Jan 2020 & Base  &  \textbf{Operations rehearsal \#3 for commissioning}
Dress rehearsal -- Just like it will be April for the actual commissioning.
	\\ \hline
Dec 2020 &  NCSA &  \textbf{Operations rehearsal data release processing (commissioning data)}
	Dress rehearsal -- Just like it will be April for the actual commissioning.
	\\ \hline

	\\ \hline

Nov 2021 &  NCSA/Base &  \textbf{Operations rehearsal}
Rehearsals for real operations which start  Nov 2021
	\\ \hline
Jan 2022 &  NCSA/Base &  \textbf{Operations rehearsal data release processing}
Full dress rehearsal for real data release
	\\ \hline

Aug 2022 &  NCSA &  \textbf{Operations rehearsal for full data release processing (if needed).}
Reconfirm operability of all updated software post commissioning.
	\\ \hline

\end{longtable}
