\subsection{Science Platform with WISE data in PDAC \textbf{(LDM-503-1)}\label{LDM-503-1}}
SUIT continues PDAC development, adding the WISE data, further exercising the DAX dbserv and imgserv APIs, and taking advantage of metaserv once it becomes available
 \newline
From DAX: need to be clear about which WISE datasets are to be loaded -- the data wrangling effort required to download, inspect, convert, partition, and load each additional dataset is cumulatively non-trivial for DAX

\input LDM-503-2

\subsection{Alert generation validation \textbf{(LDM-503-3)}\label{LDM-503-3}}
Validate the alert generation stack performance on several DECam and HSC datasets.
 \newline
"Stack" is probably ill-defined here — is this simply testing science logic, or are we going after a wider integration exercise?
\subsection{Aux Tel DAQ integration functionality test \textbf{(LDM-503-4)}\label{LDM-503-4}}
The production Aux Tel data acquisition hardware should be available in Tucson in 2018-02. We should prepare by testing the adjacent archive systems.
 \newline
A minimal DM-only system that can archive mocked-up images and demonstrate that they can be retrieved, with provenance and metadata.
\subsection{Test Report: Aux Tel DAQ interface Integration Verification and Spectrograph Operations Rehearsal \textbf{(LDM-503-4b )}\label{LDM-503-4b }}
The production Aux Tel data acquisition hardware should be available in Tucson in 2018-02. We should test integration with the adjacent archive systems.
 \newline
A minimal system that can archive simulated images from the Aux Tel DAQ and demonstrate that they can be retrieved.
\subsection{Alert distribution validation \textbf{(LDM-503-5)}\label{LDM-503-5}}
Validate alert distribution system and mini-broker fed by live or simulated live data.
 \newline
Can we test a SUIT interface to the broker at this point? I believe it's not scheduled until later in construction.
\subsection{DM ComCam interface verification readiness \textbf{(LDM-503-6)}\label{LDM-503-6}}
ComCam will be in Tucson on 2018-07-24. The DM system must be ready to deal with it.
 \newline
"The DM system" should use some further definition: what do we want to test here? Data flow from ComCam to the Data Backbone, or science processing of ComCam data?
 Note the LSE-79 requirements for DM services in support of ComCam in table 8. They're required by Nov 2019/Feb 2020; it may be more appropriate to test some of them at a later date?
\subsection{Camera data processing \textbf{(LDM-503-7)}\label{LDM-503-7}}
Partial camera data should be available to DM July 31st. We plan to test DM stack with it.
 \newline

\subsection{Spectrograph data acquisition \textbf{(LDM-503-8)}\label{LDM-503-8}}
Demonstrate that we can acquire (and process?) data from the Spectrograph.
 \newline
Per LSE-79, AuxTel delivery in Nov 2017 (ie, a year before this milestone) includes: → EFD ETL service → Aux Telescope Archiving Service → Data backbone in support of Aux Telescope archiving Do we need to schedule another test to cover that?
\subsection{Verification tests in advance of pre-ops rehearsal for commissioning \#1 \textbf{(LDM-503-9)}\label{LDM-503-9}}
Test how the system will run during commissioning.
 Chuck requests that this initial test focus on ISR.
 \newline
"Focus on ISR" — we should test whatever we have available. See LSE-79 for a list of requirements.
\subsection{DAQ validation \textbf{(LDM-503-10)}\label{LDM-503-10}}
There is a project Milestone that DAQ/DM/Networks are available March 15th. We need to run tests in Feb to show this is ready.
 \newline

\subsection{DM ComCam operations readiness \textbf{(LDM-503-11a)}\label{LDM-503-11a}}
ComCam will be in use in Nov . The DM system must be ready to deal with it.
 \newline
"The DM system" should use some further definition: what do we want to test here? Data flow from ComCam to the Data Backbone, or science processing of ComCam data?
 Note the LSE-79 requirements for DM services in support of ComCam in table 8. They're required by Nov 2019/Feb 2020; it may be more appropriate to test some of them at a later date?
\subsection{Verification tests in advance of pre-ops rehearsal for commissioning \#2 \textbf{(LDM-503-11)}\label{LDM-503-11}}
More complete commissioning rehearsal: how do the scientists look at data? How do they provide feedback to the telescope? How do we create/update calibrations?
 Exercise control loops.
 \newline

\subsection{Verification tests in advance of pre-ops rehearsal for commissioning \#3 \textbf{(LDM-503-12)}\label{LDM-503-12}}
Dress rehearsal: commissioning starts in April, so by this stage we should be ready to do everything needed.
 \newline

\subsection{Ops rehearsal DRP (ComCam data) \textbf{(LDM-503-13)}\label{LDM-503-13}}
ComCam data will now be available. Demonstrate its use in producing a data release.
 \newline
Note that LSE-79 requires a suite of DM services in support of the full camera in May 2020. It seems inappropriate to test them as part of a commissioning ops rehearsal, but they are well before this data. Do we need another test milestone?
\subsection{DM Software for Science Verification \textbf{(LDM-503-14)}\label{LDM-503-14}}
Science Verification starts in April. Demonstrate that all required DM software is available.
 \newline
SV will include calculating all KPMs to demonstrate that we are reaching the science requirements. That obviously means we'll need code which is both capable of reaching those requirements, and calculating the KPMs.
\subsection{Verification tests in advance of Full Operations rehearsal  \textbf{(LDM-503-15)}\label{LDM-503-15}}
Confirm readiness for operations.
 \newline

\subsection{Operations Rehearsal for Data Release Production  \textbf{(LDM-503-16)}\label{LDM-503-16}}
Test readiness for data release production.
 \newline

\subsection{Verification tests for full DRP \textbf{(LDM-503-17)}\label{LDM-503-17}}
Confirm readiness for data release production  with fixes from commissioning.
 \newline

